Tables/Graphs for Article

### 2018-01-02 article/draft1.tex
added new file

\documentclass{article}
\usepackage{multirow}
\begin{document}
\SweaveOpts{concordance=TRUE}

<< echo = FALSE >>=
# importing data 
dir <- file.path(getwd(),"data")
x <- read.csv(file.path(dir, "dat.csv"))

model <- rms::cph(survival::Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + sqrt(avg_tag_score) + log10(text_length) + rms::rcs(sqrt(device_length), 4) + rms::rcs(sqrt(avg_tag_length), 3) + rms::rcs(sqrt(newline_ratio), 3), data = x, x = TRUE, y = TRUE, surv = TRUE)
@

@@

Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge. Thousands of questions and answers are posted everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction, and increase web traffic. This paper presents a survival analysis of response time, or the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$). Significant predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

<< echo = FALSE >>=
# for inline code 
answered <- sum(x$answered)
percentans <- round((answered / nrow(x)) * 100, 1) 
shortest <- round(min(x$time_until_answer) * 60, 2) 
longest <- round(max(x$time_until_answer), 2)
longest_d <- round(longest / 24, 2) 
@

@@

  Of 8,025 questions in the full data set, \Sexpr{nrow(x)} were in English (97\% of the full data). Of those questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date. The shortest response time was \Sexpr{shortest} hours. The longest was \Sexpr{longest} hours (\Sexpr{longest_d} days). Figure ~\ref{fig:answertimes} shows the distribution of response times for all questions analyzed.

<< echo = FALSE >>=
# Kaplan-Meier survival estimates
surv_object <- survival::Surv(x$time_until_answer, x$answered, type = "right")
KM <- survival::survfit(surv_object ~ 1, conf.type = "log-log")

stats <- summary(KM)$table
mean <- round(unname(stats[5]), 2) 
median <- round(unname(stats[7]), 2)
@

@@

  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability for all questions in the data. The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{round(mean / 24, 2)} days. The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{median} hours. Table \ref{table:quantiles} provides additional percentiles of survival time.

@@

<< echo = FALSE >>=
set.seed(444)
splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)

train1 <- x[splitPlan[[1]]$train, ]; test1 <- x[splitPlan[[1]]$app, ]
train2 <- x[splitPlan[[2]]$train, ]; test2 <- x[splitPlan[[2]]$app, ]
train3 <- x[splitPlan[[3]]$train, ]; test3 <- x[splitPlan[[3]]$app, ]
train4 <- x[splitPlan[[4]]$train, ]; test4 <- x[splitPlan[[4]]$app, ]
train5 <- x[splitPlan[[5]]$train, ]; test5 <- x[splitPlan[[5]]$app, ]
@

Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions. Results of univariate analysis, performed on one training set, for transformed and untransformed continuous predictors, and every categorical predictor, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively. All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.

@@

<< echo = FALSE >>=
# answered question id = 397414
index <- which(x$id == 397414)

# unanswered question id = 399971
index2 <- which(x$id == 399971)
@

>>>>

\documentclass{article}
\usepackage{multirow}
\usepackage{Sweave}
\begin{document}
\input{draft1-concordance}

@@

Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge. Thousands of questions and answers are posted everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction, and increase web traffic. This paper presents a survival analysis of response time, or the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

@@

  Of 8,025 questions in the full data set, 7760 were in English (97\% of the full data). Of those questions, 4951 (63.8}\%) received an answer by the download date. The shortest response time was 0.5 hours. The longest was 2159.02 hours (89.96 days). Figure ~\ref{fig:answertimes} shows the distribution of response times for all questions analyzed.

@@

  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability for all questions in the data. The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours. Table \ref{table:quantiles} provides additional percentiles of survival time.

@@

Each training set contained 6208 questions, and each test set contained 1552 questions. Results of univariate analysis, performed on one training set, for transformed and untransformed continuous predictors, and every categorical predictor, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively. All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.

@@

### 2018-01-02 article/graphics.Rmd
added new file

### Distribution of answer times (Figure 1)

```{r}
# x$Answered <- NA
# x$Answered[x$answered == 1] <- "Answered"
# x$Answered[x$answered == 0] <- "Unanswered"

ggplot(x, aes(x = time_until_answer, fill = Answered)) +
  geom_histogram(bins = 15, alpha = 0.5, position = "identity") + 
  guides(fill = guide_legend(title = NULL)) + 
  scale_x_continuous("Time (hrs)") + 
  scale_y_continuous("Number of Questions")

@@

### KM Curve (Figure 2)

```{r}
surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
KM <- survfit(surv_object ~ 1, conf.type = "log-log")

# dashed line indicates the median survival time
ggsurvplot(KM, data = x, 
           risk.table = FALSE, 
           cumevents = FALSE, 
           conf.int = TRUE, conf.int.style = "step", 
           censor = FALSE,
           surv.median.line = "hv", 
           xlab = "Time (hours)", 
           xlim = c(0, 200), break.x.by = 20,
           ylim = c(0, 1), break.y.by = 0.1,
           surv.plot.height = 1, ggtheme = theme_bw(), 
           tables.height = 0.15, tables.theme = theme_cleantable(), fontsize = 2, na.rm = TRUE,
           legend = "none")

@@

### Table of percentiles (Table 1)

@@

trains <- list(train1, train2, train3, train4, train5)
trains <- purrr::map(trains, ~as.data.frame(.))
tests <- list(test1, test2, test3, test4, test5)
tests <- purrr::map(tests, ~as.data.frame(.))

# ---------------------------------------------------------------------------------------
get_pvalue <- function(var) { 
  formula <- paste("Surv(time_until_answer, answered) ~ ", var, sep = "")
  model <- cph(stats::as.formula(formula), data = train1)
  df <- data.frame(variable = var, 
                   pvalue = unname(model$stats[5]))
  return(df)
}
# ---------------------------------------------------------------------------------------
# categorical predictors 
categorical <- list("new_category", "new_user", "title_questionmark", 
                    "text_contain_punct", "weekday", "text_all_lower", 
                    "prior_effort", "update", "contain_unanswered", 
                    "contain_answered")
c_pvalue <- purrr::map_dfr(categorical, ~get_pvalue(.))

@@

dev_length <- list("device_length", "sqrt(device_length)") # log10 does not work 
dev_pvalue <- purrr::map_dfr(dev_length, ~get_pvalue(.))

newline <- list("newline_ratio", "sqrt(newline_ratio)") #log10 doens't work
newline_pvalue <- purrr::map_dfr(newline, ~get_pvalue(.))

tag_length <- list("avg_tag_length", "sqrt(avg_tag_length)")
taglength_pvalue <- purrr::map_dfr(tag_length, ~get_pvalue(.))

tag_score <- list("avg_tag_score", "sqrt(avg_tag_score)")
tagscore_pvalue <- purrr::map_dfr(tag_score, ~get_pvalue(.))

@@

cv_results1 <- purrr::map2(trains, tests, ~crossval(vars1, .x, .y))
avg_results1 <- get_avgmetrics(cv_results1)
avg_results1
xtable::xtable(avg_results1, caption = "Average performance metrics for training and test sets", label = "table:cv", digits = 4)
```

>>>>

### Distribution of answer times

```{r}
x$Answered <- NA
x$Answered[x$answered == 1] <- "Answered"
x$Answered[x$answered == 0] <- "Unanswered"

ggplot(x, aes(x = time_until_answer, fill = Answered)) +
  geom_histogram(bins = 15, alpha = 0.5, position = "identity") + 
  guides(fill = guide_legend(title = NULL)) + 
  scale_x_continuous("Time (hrs)") + 
  scale_y_continuous("Number of Questions") + 
  theme(text = element_text(size = 25),
        axis.text = element_text(size = 15))

@@

### KM Curve

```{r}
surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
KM <- survfit(surv_object ~ 1, conf.type = "log-log")
library(survminer)
# dashed line indicates the median survival time
ggsurvplot(KM, data = x, 
           risk.table = FALSE, 
           cumevents = FALSE, 
           conf.int = TRUE, conf.int.style = "step", 
           censor = FALSE,
           surv.median.line = "hv", 
           xlab = "Time (hours)", 
           xlim = c(0, 200), break.x.by = 20,
           ylim = c(0, 1), break.y.by = 0.1,
           surv.plot.height = 1, ggtheme = theme_bw(), 
           tables.height = 0.15, tables.theme = theme_cleantable(), fontsize = 2, na.rm = TRUE,
           legend = "none",
           font.x = 25, font.y = 25, font.tickslab = 15)

@@

### Table of percentiles

@@

trains <- list(train1, train2, train3, train4, train5)
trains <- purrr::map(trains, ~as.data.frame(.))
tests <- list(test1, test2, test3, test4, test5)
tests <- purrr::map(tests, ~as.data.frame(.))
# ---------------------------------------------------------------------------------------
get_pvalue <- function(var) { 
  formula <- paste("Surv(time_until_answer, answered) ~ ", var, sep = "")
  model <- cph(stats::as.formula(formula), data = train1)
  df <- data.frame(variable = var, 
                   pvalue = unname(model$stats[5]))
  df <- df %>% arrange(pvalue)
  return(df)
}
```

```{r}
# categorical predictors 
categorical <- list("new_category", "new_user", "title_questionmark", 
                    "text_contain_punct", "weekday", "text_all_lower", 
                    "prior_effort", "update", "contain_unanswered", 
                    "contain_answered")
c_pvalue <- purrr::map_dfr(categorical, ~get_pvalue(.))

@@

dev_length <- list("device_length", "sqrt(device_length)", "log10(device_length + 1)") 
dev_pvalue <- purrr::map_dfr(dev_length, ~get_pvalue(.))

newline <- list("newline_ratio", "sqrt(newline_ratio)", "log10(newline_ratio + 1)")
newline_pvalue <- purrr::map_dfr(newline, ~get_pvalue(.))

tag_length <- list("avg_tag_length", "sqrt(avg_tag_length)", "log10(avg_tag_length + 1)")
taglength_pvalue <- purrr::map_dfr(tag_length, ~get_pvalue(.))

tag_score <- list("avg_tag_score", "sqrt(avg_tag_score)", "log10(avg_tag_score + 1)")
tagscore_pvalue <- purrr::map_dfr(tag_score, ~get_pvalue(.))

@@

vars2 <- "new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + weekday + log10(avg_tag_score + 1) + rcs(log10(text_length), 5) + rcs(log10(avg_tag_length + 1), 4) + rcs(log10(device_length + 1), 5) + rcs(log10(newline_ratio + 1), 3)"

cv_results1 <- purrr::map2(trains, tests, ~crossval(vars1, .x, .y))
cv_results2 <- purrr::map2(trains, tests, ~crossval(vars2, .x, .y))
avg_results2 <- get_avgmetrics(cv_results2)
avg_results2
avg_results1 <- get_avgmetrics(cv_results1)
avg_results1
xtable::xtable(avg_results1, caption = "Average performance metrics for training and test sets", label = "table:cv", digits = 4)
```

```{r}
avg_results2
```
